Downward shortwave solar irradiance enhancement by clouds.

### 2024-04-17 article/article.Rmd
Commit 2024-04-17 23:14

```{r setup, echo=F, include=FALSE}
rmarkdown::find_pandoc(dir = '/usr/lib/rstudio/resources/app/bin/quarto/bin/tools')
renv::load("~/MANUSCRIPTS/02_enhancement/", quiet = TRUE)
## document configurations
knitr::opts_chunk$set(comment    = ""      )
# knitr::opts_chunk$set(dev        = "pdf"   )
knitr::opts_chunk$set(out.width  = "50%"   )
knitr::opts_chunk$set(fig.align  = "center")
# knitr::opts_chunk$set(fig.pos    = 'h!'    )
options(knitr.graphics.auto_pdf = FALSE)
library(pander)
library(data.table)
library(kableExtra)
library(dplyr)
## load data from trends analysis
source("~/MANUSCRIPTS/02_enhancement/GHI_enh_00_variables.R")
load("~/MANUSCRIPTS/02_enhancement/data/GHI_enh_03_process.Rda")
TSIinfo <- data.table(read.csv("~/MANUSCRIPTS/02_enhancement/figures/tbl_tsi_info.dat",
                               strip.white = TRUE,
                               sep = ";",
                               header = TRUE))
```

>>>>

```{r setup, echo=F, include=FALSE}
rmarkdown::find_pandoc(dir = '/usr/lib/rstudio/resources/app/bin/quarto/bin/tools')
# renv::load("~/MANUSCRIPTS/02_enhancement/", quiet = TRUE)
## document configurations
knitr::opts_chunk$set(comment    = ""      )
# knitr::opts_chunk$set(dev        = "pdf"   )
knitr::opts_chunk$set(out.width  = "50%"   )
knitr::opts_chunk$set(fig.align  = "center")
# knitr::opts_chunk$set(fig.pos    = 'h!'    )
options(knitr.graphics.auto_pdf = FALSE)
library(pander)
library(data.table)
library(kableExtra)
library(dplyr)
## load data from trends analysis
source("~/MANUSCRIPTS/02_enhancement/GHI_enh_00_variables.R")
load("~/MANUSCRIPTS/02_enhancement/data/GHI_enh_03_process.Rda")
TSIinfo <- data.table(read.csv("~/MANUSCRIPTS/02_enhancement/figures/tbl_tsi_info.dat",
                               strip.white = TRUE,
                               sep = ";",
                               header = TRUE))
```
